---
title: "Coding exercise"
author: "Nick Penzel"
date: "2025-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("Setup.R")
```


```{r}

data("knz_bison")

knz_bison -> bison


```


1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.


```{r}

bison <- bison %>% 
  mutate(age_at_obs = rec_year - animal_yob)


```

2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered data set).

```{r}

mass_filter_lessThan <- function(x) {
    filter(bison,animal_weight <= x) 
    }

#test function
less_than_mass(1000)

```


3.Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}

bison %>% 
  ggplot()+
  geom_boxplot(aes(x = animal_sex, y = animal_weight))+
  labs(title = "Comparison of Bison Mass by sex", x = "Sex", y = "Mass (lbs)")


hist(bison$animal_weight)
hist(log(bison$animal_weight))
bison %>% 
  levene_test(log(animal_weight) ~ animal_sex)

bison %>% 
  t_test(animal_weight~animal_sex, var.equal = F, detailed = F)

```

 
```

